### 2019-05-09 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Added screenshots from the documentation.
SO LONG
OK for Ch5

\TODOL{I need to write a paragraph about using the ``adversarial setting'' for piece-wise stationary. It is very important to state that EXP3.S from \cite{Auer02NonStochastic} (Section~8) achieves $\bigO{\sqrt{K \Upsilon_T T}}$ regret with NO prior knowledge of $T$ and $\Upsilon_T$.}

@@

% - Pb 1 changes are only on one arm at a time
\textbf{Problem $\bm 1$.}
We consider $K=3$ arms changing $\Upsilon_T=4$ times until $T=5000$.
The arm means $(\mu_i(t))_{1\leq i\leq K,1\leq t\leq T}$ are shown in Figure~\ref{fig:6:Problem_1}.
% (and Figure~\ref{fig:6:Problem_1} in Appendix),
Note that changes happen on only one arm (\ie, $C_T=\Upsilon_T=4$),
and the optimal arm changes once at $\tau_2^{(1)}=2000$.
%  with a large gap of $0.6$.

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_1.pdf}
    \subcaption{\textbf{Pb $1$}: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on only one arm at a time (\ie, $C=4$).}
    \label{fig:6:Problem_1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_2.pdf}
    \subcaption{\textbf{Problem $2$}: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on all arms (\ie, $C=12$).}
    \label{fig:6:Problem_2}
\end{figure}

@@

\begin{lemma}\label{lem:6:Delay}
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{lemma}
%
\begin{proof}
    It is actually not used as such in the proofs of the regret upper bound given below, but a similar result is used and proved in the proofs.
    \TODOL{We have to give the proof, or remove this result!}
\end{proof}

@@

%-----------------------------------------------------------------------------
\paragraph{Two options for restarts.}
%
For this algorithm, we simultaneously investigate two possible behavior: \emph{global restart} (reset the history of all arms once a change was detected on one of them, line $11$), and \emph{local restart} (reset only the history of the arm on which a change was detected, line $13$), which are the two different options in Algorithm~\ref{algo:6:GLRklUCB}.
%
Under local restart, in the general case the times $\tau_i(t)$ are not equal for all arms, hence the index policy associated to \eqref{def:6:UCB} is \emph{not} a standard \UCB{} algorithm, as each index uses a \emph{different exploration rate}.
%
One can highlight that in the \CUSUMUCB{} algorithm, which is the only existing algorithm based on local restart, the \UCB{} index are defined differently\footnote{~This alternative is currently not fully supported by theory, as we found mistakes in the analysis of \CUSUMUCB: Hoeffding's inequality is used with a \emph{random} number of observations and a \emph{random} threshold to obtain Eq. $(31)$-$(32)$.}:
$f(t-\tau_i(t))$ is replaced by $f(n_t)$ with $n_t = \sum_{i=1}^K n_i(t)$.

@@

\TODOL{I HAVE TO add the following algorithms, just to illustrate more Exp3.S}

\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|cccccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Problems} & Pb $1$ & Pb $2$ & Pb $3$ \\
        \hline
        Oracle-Restart \klUCB{} & $\mathbf{37 \pm 37}$ & $\mathbf{45 \pm 34}$ & $\mathbf{257 \pm 86}$ \\
        \hline
        Exp3.S & $XXX$ & $XXX$ & $XXX$ \\
        \hline
        \klUCB{} & $270 \pm 76$ & $162 \pm 59$ & $529 \pm 148$ \\
        Discounted-\klUCB{} & $1456 \pm 214$ & $1442 \pm 440$ & $1376 \pm 37$ \\
        SW-\klUCB{} & $177 \pm 34$ & $182 \pm 34$ & $1794 \pm 71$ \\
        \hline
        Thompson sampling & $493 \pm 175$ & $388 \pm 147$ & $1019 \pm 245$ \\
        DTS & $209 \pm 38$ & $249 \pm 39$ & $2492 \pm 52$ \\
        \hline
        \MklUCB{} & $290 \pm 29$ & $534 \pm 93$ & $645 \pm 141$ \\
        \CUSUMklUCB{} & $148 \pm 32$ & $152 \pm 42$ & $\mathbf{490 \pm 133}$ \\
        \hline
        \GLRklUCB{}(Local) & $\mathbf{74 \pm 31}$ & $\mathbf{113 \pm 34}$ & $513 \pm 97$ \\
        \GLRklUCB{}(Global) & $97 \pm 32$ & $134 \pm 33$ & $621 \pm 103$
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, on problems $1$, $2$ (with $T=5000$) and $3$ ($T=20000$).
    }
    \label{table:6:totalResults1}
% \end{footnotesize}
\end{table}

\begin{table}[ht]
    % \begin{small}
    \centering
    \begin{tabular}{c|cccccc}
        \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Problems} & Pb $4$ ($T=5000$) & Pb $4$ ($T=10000$) & Pb $5$ \\
        \hline
        Oracle-Restart \klUCB{} & $\mathbf{68 \pm 40}$ & $\mathbf{86 \pm 50}$ & $126 \pm 54$ \\
        \hline
        Exp3.S & $XXX$ & $XXX$ & $XXX$ \\
        \hline
        \klUCB{} & $615 \pm 74$ & $1218 \pm 123$ & $106 \pm 36$ \\
        SW-\klUCB{} & $202 \pm 33$ & $322 \pm 47$ & $228 \pm 27$ \\
        Discounted-\klUCB{} & $911 \pm 210$ & $1741 \pm 200$ & $2085 \pm 910$ \\
        \hline
        Thompson sampling & $756 \pm 65$ & $1476 \pm 137$ & $\mathbf{88 \pm 39}$ \\
        DTS & $250 \pm 39$ & $481 \pm 58$ & $238 \pm 24$ \\
        \hline
        \MklUCB{} & $337 \pm 46$ & $544 \pm 47$ & $116 \pm 36$ \\
        \CUSUMklUCB{} & $267 \pm 69$ & $343 \pm 94$ & $117 \pm 34$ \\
        \hline
        \GLRklUCB{}(Local) & $\mathbf{99 \pm 32}$ & $\mathbf{128 \pm 42}$ & $149 \pm 34$ \\
        \GLRklUCB{}(Global) & $128 \pm 32$ & $185 \pm 47$ & $152 \pm 32$
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev. Problem $4$ use $K=3$ arms, and a first long stationary sequence. Problem $5$ use $K=5$, $T=20000$ and is much harder with $\Upsilon=82$ breakpoints and $C=179$ changes.}
    \label{table:6:totalResults2}
    % \end{small}
\end{table}

>>>>

% \TODOL{I need to write a paragraph about using the ``adversarial setting'' for piece-wise stationary. It is very important to state that EXP3.S from \cite{Auer02NonStochastic} (Section~8) achieves $\bigO{\sqrt{K \Upsilon_T T}}$ regret with NO prior knowledge of $T$ and $\Upsilon_T$.}

@@

% - Pb 1 changes are only on one arm at a time
\textbf{Problem $\bm 1$.}
We consider $K=3$ arms changing $\Upsilon_T=4$ times until $T=5000$.
The arm means $(\mu_i(t))_{1\leq i\leq K,1\leq t\leq T}$ are shown in Figure~\ref{fig:6:Problem_1} below.
% (and Figure~\ref{fig:6:Problem_1} in Appendix),
Note that changes happen on only one arm (\ie, $C_T=\Upsilon_T=4$),
and the optimal arm changes once at $\tau_2^{(1)}=2000$.
%  with a large gap of $0.6$.

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_1.pdf}
    \subcaption{\textbf{Problem $1$}: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on only one arm at a time (\ie, $C=4$).
        The means are in $[0,1]$, and there are $C+1=5$ stationary intervals of equal lengths.
        Some changes do not modify the optimal arm (\eg, at $T=1000$ and $T=4000$) and others do.
    }
    \label{fig:6:Problem_1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_2.pdf}
    \subcaption{\textbf{Problem $2$}: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on all arms (\ie, $C=12$).
        The means are again in $[0,1]$, and there are also $C+1=5$ stationary intervals of equal lengths.
        % Some changes do not modify the optimal arm, but the mean of each arm does change at all change points.
    }
    \label{fig:6:Problem_2}
\end{figure}

@@

\begin{lemma}\label{lem:6:Delay}
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{lemma}
%
\begin{proof}
    It is actually not used as such in the proofs of the regret upper bound given below, but a similar result is used and proved in the proofs.
    \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{proof}

@@

%-----------------------------------------------------------------------------
\paragraph{Two options for restarts.}
%
For this algorithm, we simultaneously investigate two possible behavior: \emph{global restart} (reset the history of all arms once a change was detected on one of them, line $11$), and \emph{local restart} (reset only the history of the arm on which a change was detected, line $13$), which are the two different options in Algorithm~\ref{algo:6:GLRklUCB}.
%
Under local restart, in the general case the times $\tau_i(t)$ are not equal for all arms, hence the index policy associated to \eqref{def:6:UCB} is \emph{not} a standard \UCB{} algorithm, as each index uses a \emph{different exploration rate}.
%
One can highlight that in the \CUSUMUCB{} algorithm, which is the only existing algorithm based on local restart, the \UCB{} index are defined differently\footnote{~This alternative is currently not correctly supported by theory, as we found mistakes in the analysis of \CUSUMUCB: the main problem resides in the use of Hoeffding's inequality with a \emph{random} number of observations and a \emph{random} threshold to obtain Eq. $(31)$-$(32)$ in the paper \cite{LiuLeeShroff17}.}:
$f(t-\tau_i(t))$ is replaced by $f(n_t)$ with $n_t = \sum_{i=1}^K n_i(t)$.

@@

% \TODOL{I HAVE TO add the following algorithms, just to illustrate more Exp3.S}

\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|cccccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Problems} & Pb $1$ & Pb $2$ & Pb $3$ \\
        \hline
        Oracle-Restart \klUCB{} & $\mathbf{37 \pm 37}$ & $\mathbf{45 \pm 34}$ & $\mathbf{257 \pm 86}$ \\
        \hline
        Exp3.S & $352 \pm 51$ & $310 \pm 62$ & $665 \pm 93$ \\
        \hline
        \klUCB{} & $270 \pm 76$ & $162 \pm 59$ & $529 \pm 148$ \\
        Discounted-\klUCB{} & $1456 \pm 214$ & $1442 \pm 440$ & $1376 \pm 37$ \\
        SW-\klUCB{} & $177 \pm 34$ & $182 \pm 34$ & $1794 \pm 71$ \\
        \hline
        Thompson sampling & $493 \pm 175$ & $388 \pm 147$ & $1019 \pm 245$ \\
        DTS & $209 \pm 38$ & $249 \pm 39$ & $2492 \pm 52$ \\
        \hline
        \MklUCB{} & $290 \pm 29$ & $534 \pm 93$ & $645 \pm 141$ \\
        \CUSUMklUCB{} & $148 \pm 32$ & $152 \pm 42$ & $\mathbf{490 \pm 133}$ \\
        \hline
        \GLRklUCB{}(Local) & $\mathbf{74 \pm 31}$ & $\mathbf{113 \pm 34}$ & $513 \pm 97$ \\
        \GLRklUCB{}(Global) & $97 \pm 32$ & $134 \pm 33$ & $621 \pm 103$
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, on problems $1$, $2$ (with $T=5000$) and $3$ ($T=20000$).
    }
    \label{table:6:totalResults1}
% \end{footnotesize}
\end{table}

\begin{table}[ht]
    % \begin{small}
    \centering
    \begin{tabular}{c|cccccc}
        \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Problems} & Pb $4$ ($T=5000$) & Pb $4$ ($T=10000$) & Pb $5$ \\
        \hline
        Oracle-Restart \klUCB{} & $\mathbf{68 \pm 40}$ & $\mathbf{86 \pm 50}$ & $126 \pm 54$ \\
        \hline
        Exp3.S & $551 \pm 63$ & $860 \pm 109$ & $1723 \pm 421$ \\
        \hline
        \klUCB{} & $615 \pm 74$ & $1218 \pm 123$ & $106 \pm 36$ \\
        SW-\klUCB{} & $202 \pm 33$ & $322 \pm 47$ & $228 \pm 27$ \\
        Discounted-\klUCB{} & $911 \pm 210$ & $1741 \pm 200$ & $2085 \pm 910$ \\
        \hline
        Thompson sampling & $756 \pm 65$ & $1476 \pm 137$ & $\mathbf{88 \pm 39}$ \\
        DTS & $250 \pm 39$ & $481 \pm 58$ & $238 \pm 24$ \\
        \hline
        \MklUCB{} & $337 \pm 46$ & $544 \pm 47$ & $116 \pm 36$ \\
        \CUSUMklUCB{} & $267 \pm 69$ & $343 \pm 94$ & $117 \pm 34$ \\
        \hline
        \GLRklUCB{}(Local) & $\mathbf{99 \pm 32}$ & $\mathbf{128 \pm 42}$ & $149 \pm 34$ \\
        \GLRklUCB{}(Global) & $128 \pm 32$ & $185 \pm 47$ & $152 \pm 32$
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev. Problem $4$ use $K=3$ arms, and a first long stationary sequence. Problem $5$ use $K=5$, $T=100000$ and is much harder with $\Upsilon=82$ breakpoints and $C=179$ changes.}
    \label{table:6:totalResults2}
    % \end{small}
\end{table}
